---
title: "Reducing engagement with affectively polarised content: Main & Exploratory Analyses"
author: "Fintan Smith, Almog Simchon, Dawn Holford, Stephan Lewandowsky"
date: '2023-09-12'
output: html_document
---


```{r, include=FALSE}

#setwd('C:/Users/fintan.smith/Documents/Diss')

```

# Experiment 1 analyses

## Experiment 1: Engagement analysis

```{r engagement, include=TRUE, warning=FALSE}

library(pacman)




p_load(tidyverse, rockchalk, reshape2,rstatix,ggpubr,ez,naniar,psych, afex, PROscorerTools,
       emmeans, ggplot2, knitr, see, corrplot, lavaan, effects,interactions, wesanderson,performance,
       stargazer,mediation, vtable)

#helper functions

keep_score <- function(x){
  ifelse(x %in% c(1:4), x, NA)
}



#read data
dt <- read_csv("Data/Experiment_1_data.csv")


#recode
dt_remove_reaction <- dt %>% 
  mutate(across(scapegoating_leave_reaction:emotional_control_remain_sharing,
                keep_score))


#data wrangling
dt_analysis_remove_reaction <- dt_remove_reaction %>% 
  dplyr::select(ID, split_video, scapegoating_leave_reaction:emotional_control_remain_sharing) %>% 
  pivot_longer(-c(ID,split_video)) %>% 
  filter(!str_detect(name, "reaction")) %>% 
  mutate(derogatory = ifelse(str_detect(name, "_control_"),
                       "non_derogatory", "derogatory"),
         name = str_remove_all(name, "_control")) %>% 
  tidyr::separate(name, sep = "_", into = c("technique", "brexit", "metric")) %>% 
  filter(metric != "reaction") %>% 
    mutate(cond = ifelse(split_video==1, "Experimental", "Control")) %>% 
    dplyr::select(-split_video) %>% 
  mutate(value = 5-value) #recode values



dt_analysis_sharing <- dt_analysis_remove_reaction %>% 
  filter(metric %in% c("sharing", "click")) %>% 
  mutate(derogatory = ifelse(derogatory=="derogatory",
                             "Affective", "Issue"))


# 2x2 ANOVA
mod_1_engage <- afex::aov_ez(id = "ID",
             dv = "value",
             between = "cond",
             within = "derogatory",
             na.rm=TRUE,
             data = dt_analysis_sharing)

nice(mod_1_engage)


```
## Experiment 1: Sharing analysis


```{r, include=TRUE, warning=FALSE}

#keep sharing only
dt_analysis_sharing_only <- dt_analysis_remove_reaction %>% 
  filter(metric %in% c("sharing")) %>% 
  mutate(derogatory = ifelse(derogatory=="derogatory",
                             "Affective", "Issue"))


# 2x2 ANOVA
mod_1_share <- afex::aov_ez(id = "ID",
             dv = "value",
             between = "cond",
             within = "derogatory",
             na.rm=TRUE,
             data = dt_analysis_sharing_only)

nice(mod_1_share)

```

## Experiment 1: Clicking analysis

```{r, include=TRUE, warning=FALSE}

#keep clicking only
dt_analysis_clicking_only <- dt_analysis_remove_reaction %>% 
  filter(metric %in% c("click")) %>% 
  mutate(derogatory = ifelse(derogatory=="derogatory",
                             "Affective", "Issue"))


# 2x2 ANOVA
mod_1_click <- afex::aov_ez(id = "ID",
             dv = "value",
             between = "cond",
             within = "derogatory",
             na.rm=TRUE,
             data = dt_analysis_clicking_only)

nice(mod_1_click)



```

## Experiment 1: Impact of derogatory technique upon sharing likelihood in affectively polarised stimuli

```{r, include=TRUE, warning=FALSE}


dt_analysis_affective_only <- dt_analysis_sharing_only %>%
  filter(derogatory %in% "Affective")%>%
  filter(value >=1 & value <=4)

mod_1_technique <- afex::aov_ez(id = "ID",
                       dv = "value",
                       na.rm=FALSE,
                       type=3,
                       between = c("technique","cond"),
                       data = dt_analysis_affective_only)


nice(mod_1_technique)

```

## Experiment 1: Mediation analyses

```{r, mediation, include=TRUE, warning=FALSE}





#Read in data

df <- read.csv("Data/Experiment_1_data.csv", header=TRUE)


#Selects relevant outcome variables for analysis and wrangling and assigns to object 'cond_outcomes_df'

cond_outcomes_df <- df%>%  dplyr::select(ID, brexdentity, split_video, scapegoating_leave_reaction : emotional_control_remain_sharing,  scapegoating_leave_sharing, t1_1, t1_2, split_trials, contains("reaction"))


#replaces missing values of not sure and not asked with 'NA'   

cond_outcomes_df[cond_outcomes_df==9] <- NA   
cond_outcomes_df[cond_outcomes_df==5] <- NA  

cond_polar_df <- cond_outcomes_df%>% dplyr::select(ID, split_video, brexdentity, t1_1, t1_2, scapegoating_remain_sharing, scapegoating_leave_sharing, adhominem_leave_sharing,adhominem_remain_sharing,
                                                   emotional_leave_sharing, emotional_remain_sharing, scape_control_leave_sharing, scape_control_remain_sharing, adhom_control_leave_sharing, adhom_control_remain_sharing,
                                                   emotional_control_leave_sharing, emotional_control_remain_sharing, contains("reaction"))




#replaces missing values of not sure and not asked with 'NA'   
cond_polar_df <- cond_polar_df%>%
  replace_with_na(replace = list(scapegoating_remain_sharing=c(5,9), scapegoating_leave_sharing=c(5,9), adhominem_remain_sharing=c(5,9), adhominem_leave_sharing=c(5,9), 
                                 emotional_remain_sharing=c(5,9),emotional_leave_sharing=c(5,9), t1_1=c(999,997), t1_2=c(999,997),scape_control_leave_sharing= c(5,9), scape_control_remain_sharing= c(5,9), adhom_control_remain_sharing= c(5,9), adhom_control_leave_sharing= c(5,9),
                                 emotional_control_leave_sharing= c(5,9), emotional_control_remain_sharing = c(5,9)))


  
  
  


#Unites all derogatory sharing likelihood condition values into one variable and then codes any empty cells as NA

cond_polar_df <- cond_polar_df%>%
  unite(Derogatory_sharing, c(scapegoating_remain_sharing, scapegoating_leave_sharing, adhominem_leave_sharing, adhominem_remain_sharing, 
                              emotional_leave_sharing, emotional_remain_sharing), na.rm=TRUE, remove=TRUE)%>%
  unite(Non_derogatory_sharing, c(scape_control_leave_sharing, scape_control_remain_sharing, adhom_control_remain_sharing, adhom_control_leave_sharing,
                                  emotional_control_leave_sharing, emotional_control_remain_sharing), na.rm=TRUE, remove=TRUE)%>%
  unite(col=Polarization_score, t1_1:t1_2,na.rm=TRUE, remove=TRUE)


cond_polar_df$Polarization_score <- as.numeric(cond_polar_df$Polarization_score) 
cond_polar_df$Derogatory_sharing <- as.numeric(cond_polar_df$Derogatory_sharing)  
cond_polar_df$Non_derogatory_sharing <- as.numeric(cond_polar_df$Non_derogatory_sharing)
cond_polar_df$split_video <- as.numeric(cond_polar_df$split_video)



#Reverse coding polarization score (now 0= Warmest feeling possible | 100= coldest) and sharing (now 1=Not at all likely | 4= Very likely)

cond_polar_df <- cond_polar_df%>%
  mutate(Polarization_score= 101-Polarization_score)%>%
  mutate(Derogatory_sharing= 5-Derogatory_sharing)%>%
  mutate(Non_derogatory_sharing= 5-Non_derogatory_sharing)


# Switches round numeric codes of dummy coded conditions so 1 is control and 2 is experimental

cond_polar_df<- cond_polar_df%>%
  mutate(split_video= ifelse(split_video==1, 2,1))


#Excludes cases with NA either in the derogatory sharing measure

cond_polar_df <- cond_polar_df%>%
  filter(!is.na(Derogatory_sharing))%>%
  filter(!is.na(Polarization_score))



#sort out split video

cond_polar_df$split_video <- as.factor(cond_polar_df$split_video)



#Total effect
total_effect <- lm(Derogatory_sharing~split_video, data=cond_polar_df)

#Effect on mediator
mediator_fit <- lm(Polarization_score~split_video, data=cond_polar_df)

#Effect OF mediator (on DV)
fit_dv <- lm(Derogatory_sharing~ split_video + Polarization_score, data=cond_polar_df)


#Causal mediation

overall <- mediation::mediate(mediator_fit, fit_dv, sims=5000, treat = "split_video", mediator="Polarization_score", boot=T, robustSE = T)

summary(total_effect)
summary(mediator_fit)
summary(fit_dv)
summary(overall)


```

## Experiment 1: Reactions analysis


```{r, include=TRUE, warning=FALSE}


cond_reactions_df_long <- dplyr::select(cond_outcomes_df, ID, contains ("reaction"), split_video)



cond_reactions_df_long <- cond_reactions_df_long %>%
  replace_with_na(., replace=list("scapegoating_remain_reaction"=99, "scapegoating_leave_reaction"=99, "adhominem_leave_reaction"=99, "adhominem_remain_reaction"=99, 
                                  "emotional_leave_reaction"=99, "emotional_remain_reaction"=99,"scape_control_leave_reaction"=99, "scape_control_remain_reaction"=99, "adhom_control_remain_reaction"=99, "adhom_control_leave_reaction"=99,
                                  "emotional_control_leave_reaction"=99, "emotional_control_remain_reaction"=99))

cond_reactions_df_long <- cond_reactions_df_long%>%
  pivot_longer(contains("reaction"),
               names_to = "Condition",
               values_to = "Reaction",
               values_drop_na = T)

cond_reactions_df_long <- cond_reactions_df_long%>%
  mutate(Stimuli = ifelse(str_detect(Condition, "control"), 0, 1))%>%  #creates new variable that indicates video condition of that observation 
  mutate(Video_condition= ifelse(split_video==1, "Inoculation", "Control video"))%>%   #creates new variable that indicates video condition based on value of split_video
  mutate(angry_react= ifelse(Reaction==1, 1, 0))%>%
  mutate(wow_react= ifelse(Reaction==2, 1, 0))%>%
  mutate(sad_react= ifelse(Reaction==3, 1, 0))%>%
  mutate(Love_react= ifelse(Reaction==4, 1, 0))%>%
  mutate(like_react= ifelse(Reaction==5, 1, 0))%>%
  mutate(haha_react= ifelse(Reaction==6, 1, 0))%>%
  mutate(care_react= ifelse(Reaction==7, 1, 0))%>%
  mutate(reacted = ifelse(Reaction==8,0,1))%>%
  mutate(Stimuli = ifelse(Stimuli==1, "Derogatory", "Non derogatory"))


# Specify binomial logistic models for effect of video condition and stimuli type upon chance of selecting each reaction, and having reacted at all

angry_log_mod <- glm(angry_react~Video_condition + Stimuli + Video_condition*Stimuli,family=binomial, data=cond_reactions_df_long)
love_log__mod <- glm(Love_react ~Video_condition + Stimuli + Video_condition*Stimuli,family=binomial, data=cond_reactions_df_long)
care_log__mod <- glm(care_react ~Video_condition + Stimuli + Video_condition*Stimuli,family=binomial, data=cond_reactions_df_long)
like_log__mod <- glm(like_react ~Video_condition + Stimuli + Video_condition*Stimuli,family=binomial, data=cond_reactions_df_long)
haha_log__mod <- glm(haha_react ~Video_condition + Stimuli + Video_condition*Stimuli,family=binomial, data=cond_reactions_df_long)
sad_log__mod <- glm(sad_react ~Video_condition + Stimuli + Video_condition*Stimuli,family=binomial, data=cond_reactions_df_long)
reacted_log__mod <- glm(reacted ~ Video_condition + Stimuli + Video_condition*Stimuli,family=binomial, data=cond_reactions_df_long)

# Run models into regression tables

stargazer(reacted_log__mod, angry_log_mod,love_log__mod,care_log__mod, align = TRUE,dep.var.labels=c("Reacted","Angry reaction","Love reaction","Care reaction"),
          covariate.labels=c("Video condition","Stimuli type", "Video condition * Stimuli type"), ci=TRUE, ci.level = 0.95,single.row = FALSE, type="text")

stargazer(like_log__mod, haha_log__mod,sad_log__mod, align = TRUE,dep.var.labels=c("Like reaction","Haha reaction","Sad reaction"),
          covariate.labels=c("Video condition","Stimuli type", "Video condition * Stimuli type"), ci=TRUE, ci.level = 0.95,single.row = FALSE, type="text")




# Calculate nagelkerke R^2 to add to tables

r2_nagelkerke(angry_log_mod)
r2_nagelkerke(reacted_log__mod)
r2_nagelkerke(like_log__mod)
r2_nagelkerke(love_log__mod)
r2_nagelkerke(care_log__mod)
r2_nagelkerke(haha_log__mod)
r2_nagelkerke(sad_log__mod)



```

# Experiment 2

## Experiment 2: Engagement analysis

```{r, include=TRUE, warning=FALSE}


#read data
dt_2 <- read_csv("Data/Experiment_2_data.csv") 

keep_score_2 <- function(x){
  ifelse(x %in% c(1:10), x, NA)
}

#data wrangling
  mutate(crt_score = sum(c_across(starts_with("crt_")))) %>%
  ungroup()

dt_analysis_remove_reaction_2 <- dt_2 %>% 
    mutate(across(scapegoating_leave_sharing:emotional_control_remain_click_1,
                keep_score_2),
                crt_1_score= ifelse(CRT1==0.05,1,0), # score each crt
                crt_2_score= ifelse(CRT2==5,1,0),
                crt_3_score= ifelse(CRT3==47,1,0))%>%
                rowwise()%>%
    mutate(crt_score = sum(c_across(starts_with("crt_")))) %>% # create overall crt score
                ungroup()%>% 
  dplyr::select(ID, split_video, scapegoating_leave_sharing:emotional_control_remain_click_1,crt_score) %>% 
  pivot_longer(-c(ID,split_video,crt_score)) %>%
  filter(!str_detect(name, "reaction")) %>% 
  filter(str_detect(name,"_1"))%>%
  mutate(derogatory = ifelse(str_detect(name, "_control_"),
                       "non_derogatory", "derogatory"),
         name = str_remove_all(name, "_control")) %>% 
  tidyr::separate(name, sep = "_", into = c("technique", "brexit", "metric")) %>% 
  filter(metric != "reaction") %>% 
    mutate(cond = ifelse(split_video==1, "Experimental", "Control")) %>% 
    dplyr::select(-split_video)


#keep sharing
dt_analysis_sharing_2 <- dt_analysis_remove_reaction_2 %>% 
  filter(metric %in% c("sharing", "click")) %>% 
  mutate(derogatory = ifelse(derogatory=="derogatory",
                             "Affective", "Issue"))


# 2x2 ANOVA
mod_2_engage <- afex::aov_ez(id = "ID",
             dv = "value",
             between = "cond",
             within = "derogatory",
             na.rm=TRUE,
             data = dt_analysis_sharing_2)

nice(mod_2_engage)

# repeat the same model, adding CRT score as a covariate

mod_2_engage_crt <- afex::aov_ez(id = "ID",
             dv = "value",
             between = "cond",
             within = "derogatory",
             covariate = "crt_score",
             na.rm=TRUE,
             data = dt_analysis_sharing_2)

nice(mod_2_engage_crt)

```


## Experiment 2: Sharing analysis


```{r, include=TRUE, warning=FALSE}

 


########################################

#keep sharing only
dt_analysis_sharing_only_2 <- dt_analysis_sharing_2 %>% 
  filter(metric %in% c("sharing"))


# 2x2 ANOVA
mod_2_share <- afex::aov_ez(id = "ID",
             dv = "value",
             between = "cond",
             within = "derogatory",
             na.rm=TRUE,
             data = dt_analysis_sharing_only_2)

nice(mod_2_share)

```

## Experiment 2: Clicking analysis

```{r include=TRUE, echo=F, warning=FALSE}

#keep clicking only
dt_analysis_clicking_only_2 <- dt_analysis_remove_reaction_2 %>% 
  filter(metric %in% c("click")) 


# 2x2 ANOVA
mod_2_click <- afex::aov_ez(id = "ID",
             dv = "value",
             between = "cond",
             within = "derogatory",
             na.rm=TRUE,
             data = dt_analysis_clicking_only_2)

nice(mod_2_click)



```


## Experiment 2: Reactions analyses

```{r, include=TRUE, warning=FALSE}


# Read data in again
df_2 <- read.csv("Data/Experiment_2_data.csv", header=TRUE)


#Selects relevant variables for analysis and wrangling and assigns to 'cond_outcomes_df'

cond_outcomes_df_2 <- df_2%>%  dplyr::select(ID, brexdentity, split_video,age, profile_gender,  scapegoating_leave_sharing, t1_1, t1_2, split_trials, contains("AOT"), contains ("CRT"), contains("epistemic"), contains("NFC"), contains("sharing_1"), contains ("click_1"), contains("reaction"), contains("CRT"),contains("_identity_strength"))


#replaces missing values of not sure and not asked with 'NA'   

cond_outcomes_df_2[cond_outcomes_df_2==999] <- NA 


# Wrangling - Reactions to long form --------------------------------------


cond_reactions_df_long_2 <- dplyr::select(cond_outcomes_df_2, ID, contains ("reaction"), split_video)



cond_reactions_df_long_2 <- cond_reactions_df_long_2 %>%
  replace_with_na(., replace=list("scapegoating_remain_reaction"=99, "scapegoating_leave_reaction"=99, "adhominem_leave_reaction"=99, "adhominem_remain_reaction"=99, 
                                  "emotional_leave_reaction"=99, "emotional_remain_reaction"=99,"scape_control_leave_reaction"=99, "scape_control_remain_reaction"=99, "adhom_control_remain_reaction"=99, "adhom_control_leave_reaction"=99,
                                  "emotional_control_leave_reaction"=99, "emotional_control_remain_reaction"=99))

cond_reactions_df_long_2 <- cond_reactions_df_long_2%>%
  pivot_longer(contains("reaction"),
               names_to = "Condition",
               values_to = "Reaction",
               values_drop_na = T)

cond_reactions_df_long_2 <- cond_reactions_df_long_2%>%
  mutate(Stimuli = ifelse(str_detect(Condition, "control"), 0, 1))%>%  #creates new variable that indicates video condition of that observation 
  mutate(Video_condition= ifelse(split_video==1, "Inoculation", "Control video"))%>%   #creates new variable that indicates video condition based on value of split_video
  mutate(angry_react= ifelse(Reaction==1, 1, 0))%>%
  mutate(wow_react= ifelse(Reaction==2, 1, 0))%>%
  mutate(sad_react= ifelse(Reaction==3, 1, 0))%>%
  mutate(Love_react= ifelse(Reaction==4, 1, 0))%>%
  mutate(like_react= ifelse(Reaction==5, 1, 0))%>%
  mutate(haha_react= ifelse(Reaction==6, 1, 0))%>%
  mutate(care_react= ifelse(Reaction==7, 1, 0))%>%
  mutate(reacted = ifelse(Reaction==8,0,1))%>%
  mutate(Stimuli = ifelse(Stimuli==1, "Derogatory", "Non derogatory"))

#Effect of video condition and stimuli type on different reactions

angry_log_mod <- glm(angry_react~Video_condition + Stimuli + Video_condition*Stimuli,family=binomial, data=cond_reactions_df_long_2)
love_log__mod <- glm(Love_react ~Video_condition + Stimuli + Video_condition*Stimuli,family=binomial, data=cond_reactions_df_long_2)
care_log__mod <- glm(care_react ~Video_condition + Stimuli + Video_condition*Stimuli,family=binomial, data=cond_reactions_df_long_2)
like_log__mod <- glm(like_react ~Video_condition + Stimuli + Video_condition*Stimuli,family=binomial, data=cond_reactions_df_long_2)
haha_log__mod <- glm(haha_react ~Video_condition + Stimuli + Video_condition*Stimuli,family=binomial, data=cond_reactions_df_long_2)
sad_log__mod <- glm(sad_react ~Video_condition + Stimuli + Video_condition*Stimuli,family=binomial, data=cond_reactions_df_long_2)
reacted_log__mod <- glm(reacted ~ Video_condition + Stimuli + Video_condition*Stimuli,family=binomial, data=cond_reactions_df_long_2)

#Use interaction package to produce interaction plots from binomial logit models

angry_plot<- cat_plot(angry_log_mod, pred = Video_condition, modx = Stimuli, geom = "line", point.shape = TRUE)+ scale_color_manual(values=wes_palette("Darjeeling1",2)) + labs(y="Probability of 'angry' reaction", x="Video condition", title = "Effect of video condition and stimuli type on probability of 'angry' reaction") + theme_pubclean()
love_plot <- cat_plot(love_log__mod, pred = Video_condition, modx = Stimuli, geom = "line", point.shape = TRUE)+ scale_color_manual(values=wes_palette("Darjeeling1",2)) + labs(y="Probability of 'love' reaction", x="Video condition", title = "Effect of video condition and stimuli type on probability of 'love' reaction") + theme_pubclean()
care_plot <- cat_plot(care_log__mod, pred = Video_condition, modx = Stimuli, geom = "line", point.shape = TRUE)+ scale_color_manual(values=wes_palette("Darjeeling1",2)) + labs(y="Probability of 'care' reaction", x="Video condition", title = "Effect of video condition and stimuli type on probability of 'care' reaction") + theme_pubclean()
like_plot <- cat_plot(like_log__mod, pred = Video_condition, modx = Stimuli, geom = "line", point.shape = TRUE)+ scale_color_manual(values=wes_palette("Darjeeling1",2)) + labs(y="Probability of 'like' reaction", x="Video condition", title = "Effect of video condition and stimuli type on probability of 'like' reaction") + theme_pubclean()
haha_plot <- cat_plot(haha_log__mod, pred = Video_condition, modx = Stimuli, geom = "line", point.shape = TRUE)+ scale_color_manual(values=wes_palette("Darjeeling1",2)) + labs(y="Probability of 'haha' reaction", x="Video condition", title = "Effect of video condition and stimuli type on probability of 'haha' reaction") + theme_pubclean()
sad_plot <- cat_plot(sad_log__mod, pred = Video_condition, modx = Stimuli, geom = "line", point.shape = TRUE)+ scale_color_manual(values=wes_palette("Darjeeling1",2)) + labs(y="Probability of 'sad' reaction", x="Video condition", title = "Effect of video condition and stimuli type on probability of 'sad' reaction") + theme_pubclean()
love_plot <- cat_plot(love_log__mod, pred = Video_condition, modx = Stimuli, geom = "line", point.shape = TRUE)+ scale_color_manual(values=wes_palette("Darjeeling1",2)) + labs(y="Probability of 'love' reaction", x="Video condition", title = "Effect of video condition and stimuli type on probability of 'angry' reaction") + theme_pubclean()
reacted_plot <- cat_plot(reacted_log__mod, pred = Video_condition, modx = Stimuli, geom = "line", point.shape = TRUE)+ scale_color_manual(values=wes_palette("Darjeeling1",2)) + labs(y="Probability of any reaction", x="Video condition", title = "Effect of video condition and stimuli type on probability of any reaction") + theme_pubclean()


# Produce regression tables using stargazer


stargazer(reacted_log__mod, angry_log_mod,love_log__mod,care_log__mod, align = TRUE,dep.var.labels=c("Reacted","Angry reaction","Love reaction","Care reaction"),
          covariate.labels=c("Video condition","Stimuli type", "Video condition * Stimuli type"), ci=TRUE, ci.level = 0.95,single.row = FALSE, type="text")
                                                                                                                                                                                   
stargazer(like_log__mod, haha_log__mod,sad_log__mod, align = TRUE,dep.var.labels=c("Like reaction","Haha reaction","Sad reaction"),
          covariate.labels=c("Video condition","Stimuli type", "Video condition * Stimuli type"), ci=TRUE, ci.level = 0.95,single.row = FALSE, type="text")





r2_nagelkerke(angry_log_mod)
r2_nagelkerke(reacted_log__mod)
r2_nagelkerke(like_log__mod)
r2_nagelkerke(love_log__mod)
r2_nagelkerke(care_log__mod)
r2_nagelkerke(haha_log__mod)
r2_nagelkerke(sad_log__mod)




```
# Experiment 3 (USA)

## Experiment 3: Engagement analyses


```{r , include=TRUE, warning=FALSE}



data_3 <- read_csv("Data/Experiment_3_data.csv")

data_3_a <- data_3 %>% 
  mutate(across(ShareDerog1:ShareIssue3, as.factor)) %>% 
  mutate(across(ShareDerog1:ShareIssue3, forcats::fct_relevel, c("Very unlikely", "Unlikely", "Neither likely nor unlikely", "Likely", "Very likely"), .names = "{col}_recoded")) %>% 
  mutate(across(ShareDerog1_recoded:ShareIssue3_recoded, as.numeric)) %>% 
  filter(pid7!= "Independent") %>% 
  rowwise() %>% 
  mutate(share_derog = mean(c(ShareDerog1_recoded,ShareDerog2_recoded,ShareDerog3_recoded), na.rm=T),
         share_issue = mean(c(ShareIssue1_recoded,ShareIssue2_recoded,ShareIssue3_recoded), na.rm=T)) %>% 
  ungroup() %>% 
  pivot_longer(c(share_derog, share_issue)) %>% 
  rename(sharing = name) %>% 
  mutate(treatment = ifelse(treatment==1, "Incoculation",
                            "Control"))

data_3_b <- data_3 %>% 
  mutate(across(ShareDerog1:ShareIssue3, as.factor)) %>% 
  mutate(across(ShareDerog1:ShareIssue3, forcats::fct_relevel, c("Very unlikely", "Unlikely", "Neither likely nor unlikely", "Likely", "Very likely"), .names = "{col}_recoded")) %>% 
  mutate(across(ShareDerog1_recoded:ShareIssue3_recoded, as.numeric)) %>% 
  filter(pid7!= "Independent") %>% 
  pivot_longer(c(ShareDerog1_recoded:ShareIssue3_recoded)) %>% 
  mutate(sharing = ifelse(str_detect(name, "Derog"), "derog","issue" )) %>% 
  mutate(treatment = ifelse(treatment==1, "Incoculation",
                            "Control"))


anova_derog <- afex::aov_ez(id = "participant_id",
                            dv = "value",
                            between = "treatment",
                            within = "sharing",
                            na.rm=TRUE,
                            data = data_3_b)


nice(anova_derog)




```
# Engagement plots for all experiments

Plots based on ANOVA models for overall engagement metric for experiments 1,2 and 3.

```{r, include=TRUE, warning=FALSE}



#--------------------------------#
##########SETUP###################

pal <-  c( "#FF0000", "#00A08A")
  

make_aov <- function(d){
  
  anova_model <- afex::aov_ez(id = "ID",
                              dv = "value_z",
                              between = "cond",
                              within = "derogatory",
                              na.rm=TRUE,
                              data = d)
  
  return(anova_model)
  
}

make_emms <- function(mod, d){
  
  em <- emmeans(mod, ~ derogatory | cond)
  
  emdat <- tibble(
    derogatory = summary(em)$derogatory,
    cond = summary(em)$cond,
    engagement = summary(em)$emmean,
    uppci = summary(em)$upper.CL,
    lowci =  summary(em)$lower.CL
  )
  
  return(emdat)
  
}


mytheme <- function(legend.x = NULL, legend.y = NULL, textsize = NULL) {
  theme_bw(base_size = 12) %+replace%
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_rect(colour = "black", fill = NA),
          panel.background = element_blank(),
          text = element_text(size = textsize),
          axis.text = element_text(size = textsize),
          legend.text = element_text(size = textsize),
          legend.background = element_blank(),
          legend.position = c(legend.x, legend.y))
}

# ---------- Wrangle data for easy r bind & rescale (Z) ----------
data_a <- dt_analysis_sharing %>% 
  mutate(wave = "a",
         value_z = as.numeric(scale(value))) %>% 
  mutate(technique_clean = ifelse(str_detect(technique, "adhom"),
                                  "adhom",ifelse(str_detect(technique,"scape"),
                                                 "scape", "emotional"))) %>% 
  unite("stimuli", c(technique_clean, brexit, derogatory), remove = F)

data_b <- dt_analysis_sharing_2 %>% 
  mutate(wave = "b",
         value_z = as.numeric(scale(value)),
         ID = ID+10000) %>% 
  mutate(technique_clean = ifelse(str_detect(technique, "adhom"),
                                  "adhom",ifelse(str_detect(technique,"scape"),
                                                 "scape", "emotional"))) %>% 
  unite("stimuli", c(technique_clean, brexit, derogatory), remove = F)

data_c <- data_3_b %>% 
  dplyr::select(participant_id, treatment, sharing, value, name, pid7) %>% 
  mutate(participant_id = participant_id+10000000,
         treatment = ifelse(treatment=="Control", "Control",
                            "Experimental"),
         sharing = ifelse(sharing=="derog", "Affective", "Issue"),
         polit = ifelse(str_detect(pid7, "Republican"), "Republican", "Democrat")) %>%
  unite("stimuli", c(name, polit)) %>% 
  dplyr::rename(ID = participant_id,
         derogatory = sharing,
         cond = treatment) %>% 
  mutate(wave = "c",
         value_z = as.numeric(scale(value)))


## Make Anova models and generated EMMeans for experiments 1,2 and 3

mod_a <- make_aov(data_a)
emm_a <- make_emms(mod_a)


mod_b <- make_aov(data_b)
emm_b <- make_emms(mod_b)


mod_c <- make_aov(data_c)
emm_c <- make_emms(mod_c)



# -------- specify means plots for experiments 1,2,3 --------


m1 <- emmeans::emmip(mod_a, derogatory~cond, CIs=TRUE) +
  scale_colour_manual(values = pal) +
  mytheme(textsize = 14) +
  labs(x = "Video Condition",
       color = "Polarisation",
       y = "Engagement Likelihood") +
  scale_y_continuous(limits = c(-0.3,0.3), breaks = round(seq(-0.3,0.3,0.1),1))

m2 <- emmeans::emmip(mod_b, derogatory~cond, CIs=TRUE) +
  scale_colour_manual(values = pal) +
  mytheme(textsize = 14) +
  labs(x = "Video Condition",
       color = "Polarisation",
       y = "Engagement Likelihood") +
  scale_y_continuous(limits = c(-0.3,0.3), breaks = round(seq(-0.3,0.3,0.1),1))

m3 <- emmeans::emmip(mod_c, derogatory~cond, CIs=TRUE) +
  scale_colour_manual(values = pal) +
  mytheme(textsize = 14) +
  labs(x = 'Condition',
       color = "Polarisation",
       y = "Engagement Likelihood") +
  scale_y_continuous(limits = c(-0.3,0.3), breaks = round(seq(-0.3,0.3,0.1),1))+
  theme(legend.position = "bottom", axis.title.x = element_text("Condition")) + scale_x_discrete(labels = c("Control","Inoculation")) 





# display plot of exp 1

plot(m1)

# display plot of exp 2

plot(m2)

# display plot of exp 3

plot(m3)



```
